Adopting agile in the large: motivations, success factors and challenges

### 2013-10-30 journal/article.tex
Notes on large scale

@@

@@

A key question in the study was the definition of \emph{large scale}.
--> Ref: the XP conference

--> Case studies ??

>>>>

--> Freudenberg, S. and Sharp, H., "The Top 10 Burning Research Questions from
    Practitioners," IEEE Software, pp. 8-9, 2010.

@@

Lindvall, M., et al., "Agile Software Development in Large Organizations,"
IEEE Computer, vol. 37, pp. 26-34, 2004.

Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
Perplexed: Addison-Wesley, 2003.
Boehm, B., "Get ready for agile methods, with care," IEEE Computer, vol. 35,
pp. 64 - 69, 2002.
--> Any hints on size?? Maybe size leaning towards discipline?

@@

A key question in the study was the definition of \emph{large scale}.
--> Needs to have complexity in software design?? --> What is complexity in software?
    Is ``complexity'' an issue in agile?
    What will bring complexity into software? Not costs or the length of the
    schedule. --> Having many people will bring the complexity in terms of the
    SDM to use.
--> Some people see cost as a definition for large scale, some see code base
    size [Petersen], some see project duration [Bjarnson?]. These are all
    related, but do not relate to any specific problem. You can spend X amount
    of money, but it does not in itself make any difference if the money is
    spent in an agile way.
--> Formal definitions (EU, etc.) look at project costs or company turnover.
    These definitions do not take a standpoint on complexity of the product, so
    they do not matter in the context of SDMs.

--> Ref: the XP conference
--> [Cockburn 2003] Agile is best suitable for teams around 50 people or fewer.
--> Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
    Perplexed: Addison-Wesley, 2003. --> There might be a 50 person boundary?
    --> See Boehm also for list of
